\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
fix links and qrcodes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64953 15284696-431f-4ddb-bdfa-cd5b030d7da7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Spatial interpolation}}{
The module v.surf.rst for spatial interpolation was developed approximately 12 years 
ago, since then it was improved several times (Trac2, 2014). It is now an important part 
of GRASS GIS and is even taught at geospatial modeling courses, for example 
\url{http://courses.ncsu.edu/gis582/common/grass/interpolation_2.html}.
% TODO: move link to references

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Conclusions}}{
% TODO: review the points, it should be the highlight or something like that
% TODO: style of bullets is strange
\begin{itemize}
 \item Algorithms and models once included into GRASS GIS remain available long term.
 \item GRASS GIS development team takes care of API related updates and operating system related changes.
%% TODO: what does that mean?:
 \item Scientists are using highly specialized tools implemented by other people when having both scientific publication and source code at hand.
 \item New research and tools is build upon the existing one.
\end{itemize}
}

@@

\newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}

@@

\hrulefill

%\blocksectiontitle{Acknowledgements}
\textbf{Acknowledgments}

@@

% TODO: add proper QR codes and fix links

@@

\begin{minipage}{\qrcodesize}
\includegraphics[width=\textwidth]{./images/grass_qr.pdf}
\end{minipage}

\begin{minipage}{0.15\linewidth}
\small {\url{grass.osgeo.org}}
\end{minipage}

\begin{minipage}{\qrcodesize}
\includegraphics[width=\textwidth]{./images/grass_qr.pdf}
\end{minipage}

\begin{minipage}{0.2\linewidth}
\small {\url{grasswiki.osgeo.org}}
\end{minipage}

\begin{minipage}{0.1\linewidth}
\href{http://creativecommons.org/licenses/by-sa/4.0/}{\includegraphics[width=\textwidth]{ccbysa}}
\end{minipage}

\begin{minipage}{0.35\linewidth}
\small This poster is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License.
\end{minipage}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Spatial interpolation}}{
The module v.surf.rst for spatial interpolation was developed approximately 12 years 
ago, since then it was improved several times (Trac2, 2014). It is now an important part 
of GRASS GIS and is even taught at geospatial modeling courses, for example at North Carolina State University
\cite{ncsugis582}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Conclusions}}{

\renewcommand{\labelitemi}{\textcolor{gray}{$\bullet$}\hspace{0.5ex}}

% TODO: review the points, it should be the highlight or something like that

\begin{itemize}
 \item Algorithms and models once included into GRASS GIS remain available long term.
 \item GRASS GIS development team takes care of API related updates and operating system related changes.
%% TODO: what does that mean?:
 \item Scientists are using highly specialized tools implemented by other people when having both scientific publication and source code at hand.
 \item New research and tools is build upon the existing one.
\end{itemize}
}

@@

% \newcommand{\blocksectiontitle}[1]{\subsubsection*{\textcolor{gray}{\textsf{#1}}}}
\newcommand{\blocksectiontitle}[1]{\textbf{#1}}

@@

\textcolor{gray}{
\hrulefill
}

\blocksectiontitle{Acknowledgements}

@@

% qrencode http://grass.osgeo.org -o qr_grass.eps -t EPS
% epspdf -b qr_grass.eps qr_grass.pdf

@@

\begin{minipage}{\qrcodesize}
\includegraphics[width=\textwidth]{./images/qr_grass.pdf}
\end{minipage}
~
\begin{minipage}{0.15\linewidth}
\small {\href{http://grass.osgeo.org}{\nolinkurl{grass.osgeo.org}}}
\end{minipage}

\begin{minipage}{\qrcodesize}
\includegraphics[width=\textwidth]{./images/qr_grasswiki.pdf}
\end{minipage}
~
\begin{minipage}{0.2\linewidth}
\small {\href{http://grasswiki.osgeo.org}{\nolinkurl{grasswiki.osgeo.org}}}
\end{minipage}

\begin{minipage}{0.1\linewidth}
\href{http://creativecommons.org/licenses/by-sa/4.0/}{\includegraphics[width=\textwidth]{ccbysa}}
\end{minipage}
~
\begin{minipage}{0.35\linewidth}
\small This poster is licensed under a Creative Commons Attribution-ShareAlike 4.0 International License.
\end{minipage}
